The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-18 article.tex
Combined to sentences, to fix the grammar (closes #37)
Clarified an unclear sentence (closes #38) and added missing references

The API has hardly changed. The internals, however, have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better, using a honeycomb layout approach~\cite{FIXME}, % FIXME
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

@@

Originally, the CDK was developed as a shared library between JChemPaint and Jmol. The former
used a MVC approach with an event-passing mechanism to update the view when the model was
changed. This can cause an cascade of change events being passed around. To address,
interfaces were introduced allowing multiple implementations of the core interfaces.
% TODO: check if the interfaces have previously been defined
The IChemObjectBuilders play an important role here, allowing implementations of the
interfaces to be instantiated without the need of explicitly referencing those implementations.

>>>>

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better, using a honeycomb layout approach~\cite{FIXME}, % FIXME
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

@@

Originally, the CDK was developed as a shared library between
JChemPaint~\cite{krause2000jchempaint} and Jmol~\cite{Willighagen2007jmol,Hanson2010}.
JChemPaint used a MVC approach with an event-passing mechanism to update the view when the model was
changed. This can cause an cascade of change events being passed around. To address,
interfaces were introduced allowing multiple implementations of the core interfaces.
% TODO: check if the interfaces have previously been defined
The IChemObjectBuilders play an important role here, allowing implementations of the
interfaces to be instantiated without the need of explicitly referencing those implementations.
